---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 1000,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%")
```

# municoder

<!-- badges: start -->
<!-- badges: end -->

The goal of municoder is to allow users to programmatically navigate the municode.com API,
including all of the ordinances hosted therein.

## Installation

You can install the development version of `library(municoder)` like so:

``` r
renv::install("wcurrangroome/municoder")
```

```{r}
#| include: false

library(municoder)
library(tidyverse)
library(urbnthemes)
library(janitor)
library(tigris)

set_urbn_defaults()
options(scipen = 999999)
```

Check the spatial coverage of municode.com-listed ordinances
```{r map of municode coverage by state}
all_states = municoder::get_states()

all_clients = all_states %>%
  dplyr::pull(state_abbreviation) %>%
  purrr::discard(~ str_detect(.x, "Tribes")) %>% ## "Tribes" throws an error for some reason
  purrr::map_dfr(~ get_clients_in_state(.x))

states_sf = tigris::states(cb = TRUE, progress_bar = FALSE) %>%
  dplyr::filter(GEOID < 60) %>%
  tigris::shift_geometry() %>%
  dplyr::left_join(
    all_clients %>% dplyr::count(state_abbreviation),
    by = c("STUSPS" = "state_abbreviation"))

states_sf %>% 
  ggplot2::ggplot() +
  ggplot2::geom_sf(ggplot2::aes(fill = n)) +
  ggplot2::geom_sf(data = states_sf %>% dplyr::filter(n == 0), fill = "lightgrey") +
  ggplot2::labs(
    title = "municode.com Has Coverage across All 51 States",
    subtitle = "Number of entities listed on municode.com, by state",
    fill = "Entities with ordinances on municode.com" %>% str_wrap(30)) +
  ggplot2::scale_fill_continuous(trans = "reverse") +
  urbnthemes::theme_urbn_map()
```
Explore an ordinance's table of contents (TOC):
```{r}
## this gives us the client_id
alexandria_client_id = all_clients %>%
  dplyr::filter(state_name == "Virginia", client_name == "Alexandria") %>%
  dplyr::pull(client_id)

## this gives us `product_name`s and associated `product_id`s
alexandria_zoning_product_id = municoder::get_client_content(alexandria_client_id) %>%
  dplyr::filter(product_name == "Zoning") %>%
  dplyr::pull(product_id)

alexandria_zoning_job_id = municoder::get_jobs_latest(product_id = alexandria_zoning_product_id) %>%
  dplyr::pull(id)

## this gives us `id`s for each primary component of the zoning ordinance
municoder::get_codes_toc(
  job_id = alexandria_zoning_job_id, 
  product_id = alexandria_zoning_product_id)
```


And finally pull out the text for individual sections of an ordinance. 

We can see that the "Purpose" statements for each of Alexandria's residential zones tell us quite a bit about the rationale
for each zone. For example, we might notice that the RMF zone is the only zone with a "Purpose" statement that refers to housing
affordability--raising the question why Alexandria's other zones aren't also designed to further housing affordability--and that is
also the only zone with a "Purpose" that does not explicitly refer to a cap on unit density.
```{r}
municoder::get_codes_content(
    product_id = alexandria_zoning_product_id, 
    node_id = "ARTIIIREZORE") %>%
  dplyr::pull(id) %>%
  purrr::map_dfr(~ get_codes_content(product_id = alexandria_zoning_product_id, node_id = .x)) %>%
  dplyr::filter(
    !is.na(content),
    stringr::str_detect(heading, "Purpose")) %>%
  dplyr::pull(content)
```
